Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-06 tex/main.tex
I meant abstract not intro

\begin{abstract}
To do.
\end{abstract}

>>>>

\begin{abstract}
SMT solvers have recently been extended with finite model finding techniques.
However, these cannot cope with universal quantifiers ranging over infinite
types. This paper introduces a translation that eliminates infinite quantifiers
in axioms specifying well-behaved recursive functions, including terminating,
tail-recursive, and productive functions. An empirical evaluation confirms that
the approach works well on benchmarks from various sources. The translation is
implemented as a preprocessor in the solver CVC4.
\end{abstract}
